Questioning how Researchers Develop and Present Intrusion Detection Systems

### 2014-09-12 docs/questioning.tex
added one entry
added another entry
more entries
minor changes

\title{Questioning how Researchers Develop and Present IDS}

@@

	\multirow{11}{*}{Runtime Tainting}

@@

	\multirow{11}{*}{Policy Enforcement}

@@

@@

@@

@@

    \caption{Dynamic Detection: Comparison summary of mechanisms developed to counter {\sc cia}s.}

>>>>

\title{Questioning how Researchers Develop and Present Intrusion Detection Systems}

@@

	\multirow{13}{*}{Runtime Tainting}

@@

	\multirow{14}{*}{Policy Enforcement}

@@

	&  {\it WebJail}~\cite{VDDPJ11} & {\bf ?},{\bf ?} & $\sim$7ms & {\sc xss} \\ 

@@

	&  {\it {\sc js}and}~\cite{AVBPDP12} & {\bf ?},{\bf ?} & up to 365\% & {\sc xss}\\

@@

    &  {\it Phung et al.}~\cite{PSC09} & \xmark,{\bf ?} & 5.37\% & {\sc xss} \\
    &  {\it TreeHouse}~\cite{IW12} & {\bf ?},{\bf ?} & 757–--1218ms & {\sc xss} \\
    &  {\it Dhawan et al.}~\cite{DSG12} & \xmark,{\bf ?} & 16---114\% & {\sc xss} \\

@@

    \caption{Comparison summary of mechanisms developed to counter application attacks.}
